An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-12 EconGrowth2.Rnw
Now including a single Zambia CES spaghetti graph in the paper.

<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
cesSpaghettiGraph(nest="all", energyType="Q")
@

>>>>

<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, level=1)
@

Figure~\ref{fig:CES_Spaghetti_Graph_ZM} shows details of the resample fits for Zambia with the (kl)e nesting.

<<CES_Spaghetti_Graph_ZM, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for Zambia with the (kl)e nesting.">>=
cesSpaghettiGraph(data=subset(spagData, Country=="ZM" & nest=="(kl)e"), level=1)
@
